A Switching Planner for Combined Task and Observation Planning

### 2010-11-30 code/subarchitectures/planner.sa/trunk/src/latex/ICAPS-2011/prop-dtp.tex
few changes

Finally, we make some fairly standard assumptions. First, that
action execution and sensing occur instantaneously, and that only one
action can be applied per plan-step. Second, 
that
%it can arise that in
%some propositional states an action is applicable, and in others it is
%not. Moreover, a belief-state can assign non-zero probability to
%states where that applicability holds, and states where it does
%not. We differ
%%in situations where an action exists that is applicable in some state 
%% with non-zero probability, and not applicable in another, we differ
%from~\citeauthor{younes:littman:04}~(\citeyear{younes:littman:04}),
%because 
%%in that
%we forbid the execution of the action.
%actions that are not applicable in
%any state of the current belief.  
%Also,
unlike~\citeauthor{hoffmann:brafman:2006}~(\citeyear{hoffmann:brafman:2006}),
we incorporate a PPDDL-like default semantics, treating an action
\stochAction\ executed at $\state_i$ as if it has no effect at
states $\state$ if $\poss(\stochAction) \not\subseteq
\state$.

>>>>

Finally, we make some fairly standard assumptions. First, that action
execution and sensing occur instantaneously, and that only one action
can be applied per plan-step. Secondly, it can arise that in some
states an action is applicable, and in others it is not. Moreover, a
belief-state can assign non-zero probability to states where that
applicability holds, and states where it does not. %% We differ
%% from~\citeauthor{younes:littman:04}~(\citeyear{younes:littman:04})
%% In beliefs where an action exists that is applicable in some state 
%% with non-zero probability, and not applicable in another, we differ
%% from~\citeauthor{younes:littman:04}~(\citeyear{younes:littman:04}),
%% because 
%% in that
%% we forbid the execution of the action.
%% actions that are not applicable in
%% any state of the current belief.  
%% Also,
Unlike~\citeauthor{hoffmann:brafman:2006}~(\citeyear{hoffmann:brafman:2006}),
we incorporate a PPDDL-like default semantics, treating an action
\stochAction\ executed at $\state_i$ as if it has no effect at
states $\state$ if $\poss(\stochAction) \not\subseteq
\state$.
